---
title: "Report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(regPackage1)
```
As a project of a workshop of master of data science at University of Luxembourg, I built the [`regPackage1`](https://github.com/berserkhmdvhb/regPackage1). 
You can install this package by first installing the [devtools](https://www.r-project.org/nosvn/pandoc/devtools.html) package and then using the following syntax:

`devtools::install_github("https://github.com/berserkhmdvhb/regPackage1")`

You can explore the documentation of package I provided with 

`help(package="regPackage1")`

Also, this report is accessible as vignette of the package, which can be accessed with

`vignette(package = "regPackage1")`

(Note: I just made a meta-reference)

# Load Dataset
The dataset used for this package is [Medical Cost Personal Datasets](https://www.kaggle.com/datasets/mirichoi0218/insurance).
In order to be familiarized with the dataset, after loading the `regPackage1` package, run `?insurance_data`.

The dataset is embedded in the package, therefore by simply running the following commands one can load and display the dataset.

```{r message = FALSE, warning = FALSE}
data(insurance_data)
head(insurance_data)
summary(insurance_data)
```




